---
title: "Sup_ghana_3.Rmd"
author: "Qian Feng"
date: "2018/7/24"
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      echo=TRUE, warning=FALSE, message=FALSE,
                      tidy=TRUE)
```


##Load libraries
```{r, message=FALSE, warning=FALSE}
library("reshape2")
library("ggplot2")
library(data.table)
library(stringr)
library(readr)
library(ggplot2)
library(boot)
library(ggcorrplot)
library(reshape2)
library(dplyr)
```


## mosaic non-jump parameters estimation

Iteration stops when the major parameters del and eps change by less than 1%.

```{r}
del=c(0.025,0.0107708124133,0.00832156475074,0.00818486890568,0.00815061653993,0.00830877280993,0.0081825316222,0.00799300611965,0.00806934718714)#,0.00789335318918)
eps=c(0.1,0.201061712011,0.222051886792,0.221964782206,0.226181024216,0.221638655462,0.219652036378,0.22626176219,0.2283998284)#,0.230606330807)
test_data <- data.frame(del=del,eps=eps,iter=seq(0,8,1))
test_data_long <- melt(test_data, id="iter")  # convert to long format
test_data_long$variable <- factor(test_data_long$variable, levels=c("del", "eps"), labels=c(expression(delta), expression(epsilon)))
my.labs <- list(bquote(delta),bquote(epsilon))
#pdf(file="Ghana_nonjumppar.pdf", height=4, width=6)
ggplot(data=test_data_long,aes(x=iter, y=value, colour=variable)) + geom_line()+geom_point()+xlab("Iteration")+ylab("Estimated parameter value")+ scale_x_continuous(breaks=seq(0,8,by=1))+scale_y_continuous(breaks=seq(0,0.25,by=0.05))+scale_colour_manual(values=1:2,breaks=c("delta","epsilon"),
                      labels=my.labs)
#dev.off()

```

Stop when the major parameters del and eps change by less than 1%. So we finally choose del= 0.00806934718714, eps=0.2283998284.

Now run mosaic for different jump parameters to estimate a likelihood surface. This was also run on a HPC, the commands is given below.

```{bash, eval=FALSE, include=FALSE}
#!/bin/sh

for FILE in *.fasta; 
do for jump in $(seq 0.00 0.001 0.1); do


echo sbatch -p sysgen --job-name qian.${FILE} --account SG0011 --ntasks=1 --cpus-per-task=1 --mem=25600 --mail-user=fengq2@student.unimelb.edu.au --time=0-2:0:00 -e "slurm-%A_%a.out" --wrap=\"/vlsci/SG0011/qian-feng/MZmosaic/mosaic -seq ${FILE} -aa -group 2 db target -target target -del 0.00806934718714 -eps 0.2283998284 -rec $jump > /vlsci/SG0011/qian-feng/UniMelb_shared-master/project/mosaic_processed_data/results_jump/${FILE}_${jump}_output.log\"

sleep 1

sbatch -p sysgen --job-name qian.${FILE} --account SG0011 --ntasks=1 --cpus-per-task=1 --mem=25600 --mail-user=fengq2@student.unimelb.edu.au --time=0-2:0:00 -e \"slurm-%A_%a.out\" --wrap="/vlsci/SG0011/qian-feng/MZmosaic/mosaic -seq ${FILE} -aa -group 2 db target -target target -del 0.00806934718714 -eps 0.2283998284 -rec $jump > /vlsci/SG0011/qian-feng/UniMelb_shared-master/project/mosaic_processed_data/results_jump/${FILE}_${jump}_output.log"

echo "Job submitted!\n"

sleep 1
done
done
```


```{python, eval=FALSE, include=FALSE}
###collect jump par
###collect jump par
import glob
from collections import defaultdict

jump_llk = defaultdict(list)
for logfile in glob.glob("/Users/fengqian/Downloads/UniMelb_shared-master/project/mosaic_processed_data/results_jump/*_output.log"):
    jump = float(logfile.split("_")[-2])
    with open(logfile, 'rU') as infile:
        for line in infile:
            if "Maximum Log likelihood  =" in line:
                jump_llk[jump].append(float(line.split("=")[1].strip()))

with open("/Users/fengqian/Downloads/UniMelb_shared-master/project/mosaic_processed_data/jump_llk.csv", 'w') as outfile:
    for j in sorted(jump_llk.keys()):
        outfile.write(",".join([str(j)]+[str(l) for l in jump_llk[j]]) + "\n")
```




Lets investigate the jump log-likelihoods:

```{r}
llk <- read.table("/Users/fengqian/Downloads/UniMelb_shared-master/project/mosaic_processed_data/jump_llk.csv", sep=",", header = FALSE, fill = TRUE)

llk_matrix <- data.matrix(llk[,2:ncol(llk)])

rownames(llk_matrix) <- llk[,1]

sum_stat <- function(x,i){
  t<-x[i]
  sum(t, na.rm = TRUE)
}

llk_df <- data.frame(jump=rownames(llk_matrix),
           llk=rowSums(llk_matrix, na.rm = TRUE),
           CI.L=unlist(apply(llk_matrix, 1
              , function(x){boot.ci(boot(x, sum_stat, 1000),type="perc")$percent[[4]]} )),
           CI.R=unlist(apply(llk_matrix, 1
              , function(x){boot.ci(boot(x, sum_stat, 1000),type="perc")$percent[[5]]} )),
           stringsAsFactors = FALSE)

ggplot(llk_df, aes(x=jump, y=llk, group=1)) +
    geom_line() +
    geom_errorbar(width=.1, aes(ymin=CI.L, ymax=CI.R)) +
    geom_point(shape=21, size=3, fill="white") + 
    ylim(c(-120000,-90000))+
  ylab("Composite likelihood")+
  xlab("Jump parameters")


rownames(llk_matrix)[which.max(rowSums(llk_matrix, na.rm = TRUE))]
```

